% !TEX program = xelatex

\documentclass[10pt]{resume}
% \usepackage[top=1in, bottom=1in, left=0.75in, right=0.75in]{geometry}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hongwei(Frank) Lou}

\basicInfo{
  \email{careyuyu@outlook.com} |
  \phone{619-943-6334} |
  \linkedin[linkedin.com/in/hongwei-lou/]{https://www.linkedin.com/in/hongwei-lou/}
}

\section{Education}
\datedsubsection{\textbf{University of Southern California}}{Los Angeles, CA}
\rolesecond{\textit{M.S.} in Computer Science \textbf{GPA:} 3.7/4.0}{Aug. 2020 -- Dec. 2022}
\datedsubsection{\textbf{Virginia Tech}}{Blacksburg, VA}
\rolesecond{\textit{B.S.} in Computer Science \textbf{GPA:} 3.76/4.0}{Aug. 2015 -- Dec. 2019}

\section{Work Experience}
\datedsubsection{\textbf{PONS Incorporated} | AWS, Flutter, Docker, Typescript, Dart, Java, Python }{Remote, U.S.A}
\role{Software Engineer}{Jan. 2023 -- Present}
Brief introduction: Led a team of four in the design and development of an AI-powered remote medical ultrasound
imaging software, successfully transitioning from concept to MVP and deployment in a clinical setting, instrumental for seed funding.
\begin{itemize}

\item \textbf{Engineered RESTful APIs} using AWS Lambda, integrated with DynamoDB and S3 for efficient scan record and appointment management, supporting over 10,000 daily invocations.

\item \textbf{Contributed to develop} a sophisticated ultrasound image enhancement algorithm in Java and containerized the solution using Docker, and deployed it as a stable open API via AWS ECS and AWS Fargate, resulting in a 500\% increase in software usage.

\item \textbf{Collaborated} on a data pipeline design and implementation with the AI team, leveraging SageMaker, S3, and AWS Lambda for automated data processing of over 100,000 ultrasound images daily, significantly reducing manual
labor by 95\%.

\item \textbf{Developed and maintained} web and tablet applications with Flutter, integrating APIs and managing accounts with AWS Amplify and Cognito, resulting in daily use across three hospitals.

\item \textbf{Established a solid testing framework}, achieving 80\% code coverage through automated unit tests to ensure software reliability.

\item \textbf{Automated infrastructure stack construction}  using AWS CloudFormation, TypeScript, and AWS CDK.

\end{itemize}
\datedsubsection{\textbf{PONS Incorporated} | AWS, Flutter, Typescript, Dart, Java}{Remote, U.S.A}
\role{Software Engineer Intern}{Jul. 2022 -- Dec. 2022}
\begin{itemize}
\item \textbf{Developed AWS Lambda functions} to streamline ultrasound data workflow, enabling automated indexing, analysis, and secure data transfer, enhancing system scalability and efficiency.
\item \textbf{In collaboration with the AI team}, developed real-time scan guidance by integrating the Flutter app with the Probe SDK and AI models, achieving a 99\% accuracy rate in hospital tests.
\item \textbf{Created a standardized Flutter widget library}, enhancing project efficiency.
\item \textbf{Integrated the system with EHR platforms} using OAuth2 authentication and managed user identity with Amazon Cognito, ensuring secure and compliant healthcare data management.
\item \textbf{Configured and maintained CI/CD pipelines} for Flutter and AWS applications using CDK Pipelines and AWS CodeCommit.
\end{itemize}



\section{Projects}
\datedsubsection{\textbf{A Distributed K-V Database based on Multi-Raft} | Go, Raft}{}
\begin{itemize}
\item \textbf{Implemented the Raft consensus protocol} with features such as leader election, log replication, and compaction, along with optimizations for improved performance.
\item \textbf{Enabled dynamic configuration changes and region splitting}, with a scheduler for load balancing and read index for enhanced throughput.
\item \textbf{Developed Multi-Version Concurrency Control (MVCC)} based on the Percolator protocol.
\end{itemize}

\datedsubsection{\textbf{A Secure Data Transmission and Storage System} | Go}{}
\begin{itemize}
\item \textbf{Integrated TLS} for secure data transmission between clients and servers.
\item \textbf{Implemented AES encryption} for data at rest in file system.
\item \textbf{Managed a chain of trust} with X.509 certificates for server and client authentication.
\end{itemize}

\section{Technical Skills} 
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages:} Java, JavaScript, TypeScript, Python, Dart, C, Go, SQL, HTML/CSS
  \item \textbf{Frameworks \& Technologies:} Node.js, Spring Boot, React.js, Flutter, Kubernetes, MySQL, Nginx, Git
  \item \textbf{Cloud Development:} AWS (Lambda, S3, DynamoDB, ECS, Fargate, CloudWatch, CDK), GCP, Docker
\end{itemize}
 

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
